A survey of HTTP caching options on the open Web

### 2015-01-13 sanity/paper1.tex
hardtable fig
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@976 43ef1190-90fd-4dd7-a769-d0121f02b80e

In Figure\todo{figure with freshness breakdown}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001. We also note that it is often
prohibited to cache dataset descriptions. This is odd, since
statistics about datasets is usually costly to compute and should be
cached. The VoID specification \cite{voidnote} also notes that the
statistics are considered estimates.

>>>>

In Figure~\ref{fig:hardtable}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001. We also note that it is often
prohibited to cache dataset descriptions. This is odd, since
statistics about datasets is usually costly to compute and should be
cached. The VoID specification \cite{voidnote} also notes that the
statistics are considered estimates.

\begin{figure}[ht!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardtable.pdf}}
  \caption{Mosaic Plot. Divided by type of resource on the vertical
    axis and by the same bins as in Figure~\ref{fig:hardall} on the
    horizontal axis. }
  \label{fig:hardtable}
\end{figure}
